The problem and promise of scale in multilayer networks

### 2020-01-22 paper/manuscript.Rmd
format

## Introduction
Our understandings of ecological pattern and process are directly linked to the scale at which they are observed (Levin 1992; Allen et al 2015). Animals and landscapes are influenced across scales by higher level processes, such as climate and productivity (Field et al 2009) and lower level processes, such as species interactions and resource availability (Legendre 1993; Chave 2013). The effect of scale in ecology has been explored through species distributions (Elith et al 2009) habitat selection (Mayor et al 2007) and food webs (Sugihara et al 1989). Scale can be considered for all types of measured quantities including spatial and temporal variables, as well as behavioural variables, including sociality.

@@

Animal social network analysis is a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al 2009; Wey et al. 2008; Croft et al. 2008). Social network analyses provide insight into interspecific interactions and the structure of social communities and social network properties can influences population dynamics and evolutionary processes (Pinter-Wollman et al. 2014; Kurvers et al. 2014). Nevertheless, despite the power of traditional social network analysis, it typically considers a single scale of sociality in a given network, drastically simplifying the complexity of animal social systems (Finn et al. 2019).

Unlike traditional social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each representing different classes of individuals (e.g. male or female), types of behaviours (e.g. grooming or mating), spatial areas (e.g. local or regional), or temporal windows (e.g. daily or seasonal) (Kivela et al 2014; Porter 2018). Multilayer networks are relatively novel to describing animal behaviour studies (Finn et al. 2019; Silk et al. 2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and the complete neural network of an organism (Silk et al. 2018). The role of scale within a multilayer social network context remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.

>>>>

## Introduction
Our understandings of ecological pattern and process are directly linked to the scale at which they are observed (Levin 1992; Allen et al. 2015). Animals and landscapes are influenced across scales by higher level processes, such as climate and productivity (Field et al. 2009) and lower level processes, such as species interactions and resource availability (Legendre 1993; Chave 2013). The effect of scale in ecology has been explored through species distributions (Elith et al. 2009) habitat selection (Mayor et al. 2007) and food webs (Sugihara et al. 1989). Scale can be considered for all types of measured quantities including spatial and temporal variables, as well as behavioural variables, including sociality.

@@

Animal social network analysis is a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al. 2009; Wey et al. 2008; Croft et al. 2008). Social network analyses provide insight into interspecific interactions and the structure of social communities and social network properties can influences population dynamics and evolutionary processes (Pinter-Wollman et al. 2014; Kurvers et al. 2014). Nevertheless, despite the power of traditional social network analysis, it typically considers a single scale of sociality in a given network, drastically simplifying the complexity of animal social systems (Finn et al. 2019).

Unlike traditional social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each representing different classes of individuals (e.g. male or female), types of behaviours (e.g. grooming or mating), spatial areas (e.g. local or regional), or temporal windows (e.g. daily or seasonal) (Kivela et al. 2014; Porter 2018). Multilayer networks are relatively novel to describing animal behaviour studies (Finn et al. 2019; Silk et al. 2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and the complete neural network of an organism (Silk et al. 2018). The role of scale within a multilayer social network context remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
